### 2011-01-14 docs/slides_shortened/model.tex
Slides reduced.
Thesis further shortened..

\frame
{
	\frametitle{Franks and Noble}
	\framesubtitle{Prey}

	\begin{itemize}
		\item Prey: appearance and palatability.
		\item Palatability is fixed, using different level from 0 to 1, where 0.5 is neutrally palatable.
		\item Two genes representing external appearance, using values between 1 to 200.
		\item Euclidean distance between values represents similarity.
	\end{itemize}
}

\frame
{
	\frametitle{Franks and Noble}
	\framesubtitle{Predator}

	\begin{itemize}
		\item Monte Carlo reinforcement learning system.
		\item Predators use generation on the basis of experience.
		\item Decision for consumption of prey:
		\begin{itemize}
			\item Use: set of probability formula.
			\item Dependence on phenotype.
		\end{itemize}
	\end{itemize}
}

@@

	\begin{itemize}
		\item First Experiment:
			\begin{itemize}
				\item 20 unpalatable prey species.
				\item Hypothesis 1 of a single large ring did was not established.
				\item Multiple mimicry rings exist with different frequency.
			\end{itemize}
		\item Second Experiment:
			\begin{itemize}
				\item Some palatable and some unpalatable species.
				\item Reaches condition of Batesian mimicry. 
				\item Hypothesis 2 is established.
				\item \textbf{Observation:}
					\begin{itemize}
						\item Batesian mimics provide pressure on mutants.
						\item Batesian pressure on mimicry rings push one into the range of another.
					\end{itemize}
			\end{itemize}
	\end{itemize}
}

@@

\frame
{
	\frametitle{The Predator}
	\framesubtitle{Hebbian Learning}

	\begin{itemize}
		\item Initially all weights are set to zero.
		\item Use Hebbian rule to calculate outer product of input-output vector pair, for each pair.
		\item The Outer vector matrix of all the patterns are summed to come up with the final weight matrix.
	\end{itemize}

Each component of the weight matrix \(\textbf{W} = \{w_{ij}\}\) is given by:
\begin{equation}
w_{ij} = \sum_{p=1}^{P} s_i(p) t_j(p), i \neq j
%\label{eq:}
\end{equation}
\[
w_{ij} = 0, i = j
\]
where P is the number of patterns. Vectors \textbf{S} and \textbf{T} are respectively, the input and the desired output of the network.

>>>>

\frame
{
	\frametitle{Franks and Noble}
	\framesubtitle{Prey and Predator}

\begin{itemize}
	\item Prey:
		\begin{itemize}
			\item Appearance and palatability.
			\item Palatability is fixed, using different level from 0 to 1, where 0.5 is neutrally palatable.
			\item Two genes representing external appearance, using values between 1 to 200.
			\item Euclidean distance between values represents similarity.
		\end{itemize}	
	\item Predator:
		\begin{itemize}
			\item Monte Carlo reinforcement learning system.
			\item Decision for consumption of prey:
			\begin{itemize}
				\item Use: set of probability formula.
				\item Dependence on phenotype.
			\end{itemize}
		\end{itemize}
\end{itemize}

@@

	\begin{itemize}
		\item Hypothesis 1 of a single large ring did was not established.
		\item Hypothesis 2 is established.
		\item \textbf{Observation:}
			\begin{itemize}
				\item Batesian mimics provide pressure on mutants.
				\item Batesian pressure on mimicry rings push one into the range of another.
			\end{itemize}
	\end{itemize}
}

@@

### 2011-01-14 docs/slides_shortened/parameter.tex
Slides reduced.
Thesis further shortened..

\section{Appendix: Simulation Parameters}

@@

>>>>

\section{Appendix}

@@

\frame
{
	\frametitle{The Predator}
	\framesubtitle{Hebbian Learning}

	\begin{itemize}
		\item Initially all weights are set to zero.
		\item Use Hebbian rule to calculate outer product of input-output vector pair, for each pair.
		\item The Outer vector matrix of all the patterns are summed to come up with the final weight matrix.
	\end{itemize}

Each component of the weight matrix \(\textbf{W} = \{w_{ij}\}\) is given by:
\begin{equation}
w_{ij} = \sum_{p=1}^{P} s_i(p) t_j(p), i \neq j
%\label{eq:}
\end{equation}
\[
w_{ij} = 0, i = j
\]
where P is the number of patterns. Vectors \textbf{S} and \textbf{T} are respectively, the input and the desired output of the network.
